Technique for \earlywarning\ detection of compact binary coalescence and its implication for multi-messenger astronomy

### 2011-06-03 method.tex
Minor edit
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@885 ccdd05d5-56c1-461a-bf98-85f6876523b4

In the remainder of this section we explore a method for reducing the
computational cost of a time domain search for compact binary coalescence.  We
will show that it is possible to have a theoretically zero latency algorithm
that competes with the computational cost of the standard frequency domain
matched filtering, which requires a signficant latency in order to be
computationally cheap. Our method, \lloid\ involves two transformations to the
template waveforms that produce a set of orthogonal filters with far fewer
sample points than the original template waveforms.  The reduction in the
number of sample points in all of the filters required to search the entire
parameter space is dramatic.

>>>>

In the remainder of this section we explore a method for reducing the
computational cost of a time domain search for compact binary coalescence.  We
will show that it is possible to have a theoretically zero latency algorithm
that competes with the computational cost of the standard frequency domain
matched filtering, which requires a signficant latency in order to be
computationally cheap. Our method, \lloid\ involves two transformations of the
template waveforms that produce a set of orthogonal filters with far fewer
sample points than the original template waveforms.  The reduction in the
number of sample points in all of the filters required to search the entire
parameter space is dramatic.
